LAGOS lake depth

### 2020-02-17 figures/01_geometry.Rmd
add slope comparison figure

```{r }
# compare inlake slope against buffer slope

dt         <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
hypso_pred <- read.csv("../data/00_hypso/hypso_predictors.csv", 
                       stringsAsFactors = FALSE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
dt <- left_join(dt, dplyr::select(hypso_pred, lagoslakeid, reservoir_class, 
                                  buffer100m_slope_mean), 
                                  by = c("llid" = "lagoslakeid"))

plot(dt$inlake_slope, dt$buffer100m_slope_mean/10, 
     xlim = c(0, 3), ylim = c(0, 3))
abline(0, 1)

# View(arrange(dt, buffer100m_slope_mean))

>>>>

```{r slope-compare, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# compare inlake slope, buffer slope, and online slope
# setwd("figures") 
bp <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
dt <- read.csv("../data/00_geometry/nearshore.csv", stringsAsFactors = FALSE) %>%
  mutate(llid = as.character(llid))
dt <- left_join(dt, st_drop_geometry(bp), 
                by = "llid") %>%
  dplyr::filter(!is.na(inlake_slope_mean))

# jsta::jheatmap(dt)
jsta::jheatmap(
  dplyr::select(dt, 
                slope_online_mean,
                inlake_slope_mean,
                slope_mean, 
                slope_mean_ne,
                dist_deepest, 
                dist_viscenter, 
                maxdepth,
                meandepth))

GGally::ggpairs(dplyr::select(dt, 
                inlake_slope_mean, inlake_slope.y,
                slope_online_mean,
                slope_mean, 
                # dist_deepest, 
                # dist_viscenter, 
                maxdepth), 
                progress = FALSE, 
                ) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), 
          strip.text.y = element_text(angle = 0))

gg_scatter_slope <- function(x, y, dt){
  ggplot(data = dt) + 
    geom_point(aes(UQ(rlang::sym(x)), UQ(rlang::sym(y))))
}

# dt[22,]
# which(dt$inlake_slope.y > 0.4)
# which(dt$inlake_slope.x > 0.4)
dt <- dplyr::filter(dt, inlake_slope.y < 0.4)

cowplot::plot_grid(
  gg_scatter_slope("slope_mean", "maxdepth", dt),
  gg_scatter_slope("inlake_slope.y", "maxdepth", dt), 
  gg_scatter_slope("slope_mean", "inlake_slope.y", dt)
  )
```

```{r buffer-vs-inlake_slope, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=4}
lgus_pred <- read.csv("../data/lagosus_depth_predictors.csv", stringsAsFactors = FALSE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
test <- left_join(dt, lgus_pred, by = c("llid" = "lagoslakeid")) %>%
  dplyr::filter(shape_class != "neither")

cowplot::plot_grid(
ggplot(data = test) + 
    geom_point(aes(slope_mean, inlake_slope.y, color = reservoir_class)) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "") + 
  theme(axis.title.x = element_blank()),
ggplot(data = test) + 
    geom_point(aes(slope_mean, inlake_slope.y, color = shape_class)) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = ""), 
nrow = 2 
)
```
